---
title: "week 4 part 1 - CI & T Tests"
author: "Kat Cotti"
date: "10/28/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1. Confidence Intervals 

```{r}
otter_length <- c(38, 41, 50, 27, 32, 41, 48, 60, 43) #Create a vector for your sample - impt in actual research look at data visually to make sure a t-distribution & CI will make sense to describe pop 

t.test(otter_length) #Create a t-test 
```
- T.test --> mean of sample (most meaningful thing from output), gives a 95% confidence interval (means in that % of samples we would expect to find the population mean within the range given)
- How to report: give mean with n (sample size). and standard deviation (calculate using sd), then give 95% confidence interval 
- top 3 lines --> testing that the null hypothesis is mean = 0. This doesn't make sense/ is not meaningful!! 

## T-Test (1-sample t-test)

See a claim that the mean otter length = 50 inches. Use our sample above to test this claim 

```{r}
otter_test <- t.test(x = otter_length, mu = 50)
otter_test
```
- tests null hypothesis that is meaningful! 
- p-value -->  if the pop mean is 50 inches then there is a 4.44% chance that you could have randomly taken a sample from a population that has a mean at least as different from 50 as my sample mean is in either direction

## Two- Sample t-test

```{r}
desert_bighorns <- c(32, 44, 18, 26, 50, 33, 42, 20) #Create vector of sample1
sierra_bighorns <- c(28, 31, 40, 42, 26, 29, 31) #create vectore for sample 2

t.test(x = desert_bighorns, y = sierra_bighorns)
```
- Gives means of both samples in the order of vectors inputted
- Gives confidence interval for the difference of means (mean y - mean x) --> we expect the difference in means between these two samples to be between these values 95% of the time
- t-test null = difference in means = 0, populations have equal means, alternative --> populations have unequal means 
  - t value = how far the difference in sample means is away from the null 
  - p-value = if these samples are drawn from populaitons with the same mean (null hypothesis), then there is a p-value chance that i could have taken two random samples and found sample means at least as different as the sample means i have here 
